---
title: "atlantic_flower_invertebrate_interactions - Atlantic flower–invertebrate interactions: A data set of occurrence and frequency of floral visits"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{atlantic_flower_invertebrate_interactions - Atlantic flower–invertebrate interactions: A data set of occurrence and frequency of floral visits}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Dataset used

- `atlantic_flower_invertebrate_interactions`

# Introduction

The `atlantic_flower_invertebrate_interactions` data set contains 

# Data exploration

# Citations

Boscolo et al. 2022. Atlantic flower–invertebrate interactions: A data set of occurrence and frequency of floral visits. *Ecology*, 104(3), e3900. https://doi.org/10.1002/ecy.3900

# How we processed the raw data

Download data from Ecology

```{r eval=FALSE}
# download
# download data from https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/ecy.3900

# unzip
unzip(zipfile = "data-raw/ecy3900-sup-0001-data_s1.zip", exdir = "data-raw")
```

Data cleaning
```{r eval=FALSE}
# fix data
atlantic_flower_invertebrate_interactions <- readr::read_csv("data-raw/AtlanticForestInvertFloInteractionData_2022-07.csv") %>%
    janitor::clean_names()
```
